Network Configuration Synthesis with Abstract Topologies \vspace{1cm}

### 2017-03-15 paper/abstraction/appendix.tex
checkpoint

\begin{figure*}[h!]\small
  \begin{minipage}[t]{.45\linewidth}
  \hdr{Propane/AT Syntax}{}
  \vspace*{-1\baselineskip}
  %
  \[ \begin{array}{rclr}
     pol     &::=& p_1, \dots, p_n & \textit{policies} \\
     p       &::=& t \hspace{.3em} \Path \hspace{.3em} r_1 \Prefer \dots \Prefer r_m \BNFALT cc & \textit{constraints} \\
     pfx     &::=& d.d.d.d/[d..d] & \textit{prefix} \\
     t       &::=& \$x & \textit{template variable} \\
         &\BNFALT& pfx & \textit{prefix test} \\
     r       &::=& l & \textit{location} \\
         &\BNFALT& \emptyset & \textit{empty set} \\
         &\BNFALT& \In & \textit{internal loc} \\
         &\BNFALT& \Out & \textit{external loc} \\
         &\BNFALT& r_1 \cup r_2 & \textit{union} \\
         &\BNFALT& r_1 \cap r_2 & \textit{intersection} \\
         &\BNFALT& r_1 \cdot r_2 & \textit{concatenation} \\
         &\BNFALT& \NOT r & \textit{path negation} \\
         &\BNFALT& r^* & \textit{iteration} \\
     cc     &::=& agg(pfx, r_1 \rightarrow r_2)  & \textit{control constraints} \\
  \end{array} \]%

@@

%\begin{lem}
%  For every state $N = (L, q_1, \dots, q_n)$ in $PG^A$, there exists a state $n = (l,q_1, \ldots, q_n)$ in $PG$
%  such that $f_{pg}(n) = N$.%

%  \begin{proof}
%    By assumption, we assumed that $f$ is surjective. That is, every location $L$ in the original abstract topology $G^A$ is mapped to by at least one location $l$ in the concrete topology $G$: $f(l) = L$. 
%  \end{proof}
%\end{lem}

@@

\begin{lem}

@@

  \[ \begin{array}{l}
     ~~~~~~~~~ [~ pfx \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A, \\
     ~~~~~~~~~~~~~~~~~~ pin = \mathit{adjIn}(PG^A,M), \\
     ~~~~~~~~~~~~~~~~~~ (in,q_N) \in \{(BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{b ~\vert~ b \in f^{-1}(B),~ (b,\ell) \in G.E,~ (B,q_N) \in pin \} \}), \\
     ~~~~~~~~~~~~~~~~~~ out \leftarrow \{ c ~\vert~ c \in f^{-1}(C), (c,\ell) \in G.E, (C,\_) \in \mathit{adjOut}(PG^A,M) \}, \\
     ~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A(M) : (in,q_N) \rightarrow (out,q_M) ~] \\
  \end{array} \]%

@@

  \[ \begin{array}{l}
     ~~~~~~~~~ [~ pfx \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ m \leftarrow (l,q_M) \in PG, \\
     ~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG,m), \\
     ~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (bs,q_N) ~\vert~ (\_,q_N) \in I, bs=\{ b ~\vert~ (b,q_N) \in pin\} \}), \\
     ~~~~~~~~~~~~~~~~~~ out \leftarrow \{ c ~\vert~ (c,\_) \in \mathit{adjOut}(PG,m) \}, \\
     ~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A(f_{pg}(m)) : (in,q_N) \rightarrow (out,q_M) ~] \\
  \end{array} \]%

  \begin{proof}
    For each $M$ there exists at least one $m$ such that $f_{pg}(m) = M$. Note that $f_{pg}$ overapproximates the connectivity of the product graph, by virtue of being a graph homomorphism. For each concrete node $n$ such that $n = (b,q_n) \in adjIn(PG,m)$ we know that if $f_{pg}(n) = N$ where $N = (f(b),q_N)$, then $N \in adjIn(PG^A,M)$ and $q_n = q_N$ from the homomorphism. Thus by taking $f^{-1}(B) = f^{-1}(f(b))$, for each such $f(b)$ for node $N$ that shares the same state $q_N$, we get a superset of the locations from the concrete graph. However, by restricting those locations to only those that appear in the topology $(b,\ell)$, we get exactly the set that appears in the concrete product graph. 
    This is because we know $q_N \rightarrow q_M$ from the abstract product graph is a valid transition, which means that $q_n \rightarrow q_m$ is a valid concrete product graph transition, and if there is a topology edge $(b,\ell)$, then there must be a product graph edge $(n,m)$. Therefore:
    $$\{b ~\vert~ b \in f^{-1}(B),~ (b,\ell) \in G.E,~ (B,q_N) \in \text{adjIn}(PG^A,f_{pg}(m)) \}$$
    is equivalent to
    $$\{ b ~\vert~ (b,q_N) \in \text{adjIn}(PG,m)\}$$
    This also holds for the case with adjOut. Further, note that because we are looking at a particular location $l$, there can only be at most one such $m = (l,q_N)$ such that $f_{pg}(m) = M = (f(l), q_N)$. If there is no such $m$ where $f_{pg}(m) = M$, then the above expression will produce the empty set after filtering with the topology. Going over each $M$ then is equivalent to going over each $m$ so long as we throw away imports $\mathit{in}$ that are empty.

@@

\begin{thm}
  For any context $\Gamma$, concrete topology $G$, abstract topology $G^A$, homomorphism $f : G \rightarrow G^A$:

>>>>

\begin{figure*}[h!]\small
  \begin{minipage}[t]{.45\linewidth}
  \hdr{Propane/AT Syntax}{}
  \vspace*{-1\baselineskip}
  %
  \[ \begin{array}{rclr}
     pol     &::=& p_1, \dots, p_n & \textit{policies} \\
     p       &::=& t \hspace{.3em} \Path \hspace{.3em} r_1 \Prefer \dots \Prefer r_m & \textit{constraints} \\
     pfx     &::=& d.d.d.d/[d..d] & \textit{prefix} \\
     t       &::=& \$x & \textit{template variable} \\
         &\BNFALT& pfx & \textit{prefix test} \\
     r       &::=& l & \textit{location} \\
         &\BNFALT& \emptyset & \textit{empty set} \\
         &\BNFALT& \In & \textit{internal loc} \\
         &\BNFALT& \Out & \textit{external loc} \\
         &\BNFALT& r_1 \cup r_2 & \textit{union} \\
         &\BNFALT& r_1 \cap r_2 & \textit{intersection} \\
         &\BNFALT& r_1 \cdot r_2 & \textit{concatenation} \\
         &\BNFALT& \NOT r & \textit{path negation} \\
         &\BNFALT& r^* & \textit{iteration} \\
  \end{array} \]%

@@

%\begin{lem}
%  For every state $N = (L, q_1, \dots, q_n)$ in $PG^A$ for which there is no edge $(start^A, N)$, there exists a state $n = (l,q_1, \ldots, q_n)$ in $PG$
%  such that $f_{pg}(n) = N$.
%  \begin{proof}
%    By assumption, we know that that $f$ is surjective. That is, every location $L$ in the original abstract topology $G^A$ is mapped to by at least one location $l$ in the concrete topology $G$: $f(l) = L$. %

%    Since there exists an $l$ such that $f(l) = L$, there must be the concrete node $(l, q_1, \ldots, q_n)$ in $PG$.%
%

%    %If $N$ is a node in $PG^A$ that is is not connected to the $start^A$ node, then no automata state is the initial state $q_i \neq q_{0_i}$. This means that that N must have at least one inbound edge that is not $start^A$, otherwise the node would not exist. Without loss of generality, assume there is an edge $(M,N)$ for $M = (L', s_1, \ldots, s_n)$.
%  \end{proof}
%\end{lem}

@@

In this section, we aim to prove that concretization and compilation commute for individual \sysname constraints. Since a policy is simply an ordered sequence of constraints, it is then straightfoward to show that compilation and concretization commute for entire policies. In particular, we are interested in showing:
%
$$\Con(\Compile(p, G^A), \Gamma, f, G) = \Compile(\Con(p,\Gamma,f), G)$$
%
The proof goes by case analysis on the test $t$ in the constraint $p$, and makes heavy use of the lemmas about the product graphs from the previous section. We use one helper lemma here that relates sets of neighbors:

\todo{re evaluate this. I believe we need the proof of an inverse here}
\begin{lem}

@@

  \[ \begin{array}{l}
     ~~~~~~~~~ [~ pfx \rightarrow [~ ma~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A, \\
     ~~~~~~~~~~~~~~~~~~ pin = \mathit{adjIn}(PG^A,M), \\
     ~~~~~~~~~~~~~~~~~~ (in,q_N) \in \{(BS,q_N) ~\vert~ BS=\{b ~\vert~ b \in f^{-1}(B),~ (b,\ell) \in G.E,~ (B,q_N) \in pin \}, BS \neq \emptyset  \}, \\
     ~~~~~~~~~~~~~~~~~~ out \leftarrow \{ c ~\vert~ c \in f^{-1}(C), (c,\ell) \in G.E, (C,\_) \in \mathit{adjOut}(PG^A,M) \}, \\
     ~~~~~~~~~~~~~~~~~~ ma = ord^A(M) : (in,q_N) \rightarrow (out,q_M) ~] ~] \\
  \end{array} \]%

@@

  \[ \begin{array}{l}
     ~~~~~~~~~ [~ pfx \rightarrow [~ ma ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ m \leftarrow (l,q_m) \in PG, \\
     ~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG,m), \\
     ~~~~~~~~~~~~~~~~~~ (in,q_n) \leftarrow \{ (bs,q_n) ~\vert~ bs=\{ b ~\vert~ (b,q_n) \in pin\}, bs \neq \emptyset \}), \\
     ~~~~~~~~~~~~~~~~~~ out \leftarrow \{ c ~\vert~ (c,\_) \in \mathit{adjOut}(PG,m) \}, \\
     ~~~~~~~~~~~~~~~~~~ ma = ord^A(f_{pg}(m)) : (in,q_n) \rightarrow (out,q_m) ~] ~] \\
  \end{array} \]%

  \begin{proof}
    $ $
    \vspace{.4em}

    Suppose for node $M$, there exists a node $m=(l,q_m)$ such that $f_{pg}(m) = M$. 
    We observe the following superset relation:
    %
    $$\{ b ~\vert~ (b,q_n) \in \text{adjIn}(PG,m)\} \subseteq \{ b ~\vert~ (b,l) \in G.E \}$$
    %
    This is trivially true from the definition of the product graph. Any product graph edge will correspond to a topology edge. The following inequality will also hold:
    %
    $$\{b ~\vert~ b \in f^{-1}(B),~ (B,q_N) \in \text{adjIn}(PG^A,f_{pg}(m)) \} \supseteq \{ b ~\vert~ (b,q_N) \in \text{adjIn}(PG,m)\}$$
    %
    Since whenever $(b,q_N) \in adjIn(PG,m)$ it must be the case that $(B,q_N) \in adjIn(PG^A, f_{pg}(m))$ by the homomorphism, and because $f^{-1}(B) \supseteq \{ b \}$. By combining these observations, we can conclude the following:
    %
    $$\{b ~\vert~ b \in f^{-1}(B),~ (b,\ell) \in G.E,~ (B,q_N) \in \text{adjIn}(PG^A,f_{pg}(m)) \}$$
    is equivalent to
    $$\{ b ~\vert~ (b,q_N) \in \text{adjIn}(PG,m)\}$$
    %
    The same reasoning can be applied to adjOut as well. 
    Further, note that because we are looking at a particular location $l$, there can only be at most one such $m = (l,q_N)$ such that $f_{pg}(m) = M = (f(l), q_N)$ since the automata are deterministic. 
    %
    This means that $M \leftarrow (l,q_M) \in PG^A$ can be replaced with $m \leftarrow (l,q_m) \in PG$ since for each $M$ we will either have some $m$ such that $f_{pg}(m) = M$ and the above equivalence holds, or else there is no such $M$, in which case the set is filtered by the condition: $BS \neq \emptyset$.

@@

\begin{thm}
  For all \sysname constraints $p$, contexts $\Gamma$, topologies $G$ and $G^A$ related by homomorphism $f : G \rightarrow G^A$:
  $$\Con(\Compile(p,G^A),\Gamma,f,G) = \Compile(\Con(p,\Gamma,f),G)$$

  \begin{proof} From the grammar, we know that $p = (t \Path~ r_1 ~\Prefer~ \ldots ~\Prefer~ r_n)$. The proof proceeds by cases on $t$. In each case, we expand the definition of $\Compile$ and $\Con$ until they no longer appear in the term. We then appeal to graph properties of $PG$ and $PG^A$ to rewrite the terms into equivalent forms.

  \vspace{.4em}
  \textbf{Case} ($t = pfx$)
  \vspace{.4em}

    For the right side:

    \[
    \begin{array}{llll}
      & & \Compile(\Con(p,\Gamma,f),G) \\
      &=& \Compile(\Con(pfx \Path~ r_1 ~\Prefer~ \ldots ~\Prefer~ r_n, \Gamma,f), G) 
            & \text{Substitution} \\
      &=& \Compile(pfx \Path~ \Con(r_1,\Gamma,f) ~\Prefer~ \ldots ~\Prefer~ \Con(r_n, \Gamma,f), G) 
            & \text{Definition of con} \\
      &=& \Compile(pfx \Path~ \Con(r_1,\Gamma,f) \cap \EndR(\Sigma) ~\Prefer~ \ldots ~\Prefer~ \Con(r_n, \Gamma,f) \cap \EndR(\Sigma), G) 
            & \text{Regex Equivalence}\\
      &=& \CompileMbgp([\CompilePg(pfx \Path~ \Con(r_1,\Gamma,f) \cap \EndR(\Sigma) ~\Prefer~ \ldots ~\Prefer~ \Con(r_n, \Gamma,f) \cap \EndR(\Sigma),G)]) 
            & \text{Definition of compile} \\

      &=& \CompileMbgp([(pfx, PG, \Pref)]) 
            & \text{Assumption} \\

    \end{array}
    \]

    Similarly, for the left side:

        \[
    \begin{array}{llll}
      & & \Con(\Compile(p,G^A),\Gamma,f,G) \\
      &=& \Con(\Compile(pfx \Path~ r_1 ~\Prefer~ \ldots ~\Prefer~ r_n,G^A),\Gamma,f,G)
            & \text{Substitution} \\
      &=& \Con(\CompileMbgp([\CompilePg(pfx \Path~ r_1 ~\Prefer~ \ldots ~\Prefer~ r_n,G^A)]),\Gamma,f,G)
            & \text{Definition of Compile} \\
      &=& \Con(\CompileMbgp([(pfx,PG^A,\Pref^A)]),\Gamma,f,G)
            & \text{Assumption}\\
    \end{array}
    \]

    Both sides of the equality are now in a form where we can apply the lemmas from the previous section.
    This allows us to relate $PG$ and $PG^A$ as well as $\Pref$ and $\Pref^A$.
    Continuing to expand the right side by substituting the definition of $\CompileMbgp$ we get:

  \[ \begin{array}{l}
     ~~~~~ [~ l \rightarrow rc ~\vert~ \\
     ~~~~~~~~~~~~ l \in internal(G.V), ~rc =  \\
     ~~~~~~~~~~~~~~~ [~ pfx \rightarrow [~ ma ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~~~~ m \leftarrow (l,q_m) \in PG, \\
     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG,m), \\
     ~~~~~~~~~~~~~~~~~~~~~ (in,q_n) \leftarrow \{ (bs,q_n) ~\vert~ bs=\{b ~\vert~ (b,q_n) \in pin \}, bs \neq \emptyset \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_i,m) \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ ma = \Pref(m) : (in,q_n) \rightarrow (out,q_m) ~] ~] ~]\\
  \end{array} \]%

  Next we further expand on the left side for the abstract topology to show it is equivalent:

  \[ \begin{array}{l}
     ~~~~~ \Con([~ l \rightarrow rc ~\vert~ \\
     ~~~~~~~~~~~~ l \in internal(G^A.V), ~rc =  \\
     ~~~~~~~~~~~~~~~ [~ pfx \rightarrow [~ ma ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A, \\
     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A,M), \\
     ~~~~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ BS=\{B ~\vert~ (B,q_N) \in pin \}, BS \neq \emptyset \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A,M) \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ ma = \Pref^A(M) : (in,q_N) \rightarrow (out,q_M) ~] ~] ~], \Gamma, f, G) \\
  \end{array} \]%

  We apply the definition of $\Con$ to push it inside the list:

    \[ \begin{array}{l}
     ~~~~~ [~ \ell \rightarrow \Con(rc, \ell, \Gamma, f, G) ~\vert~ \\
     ~~~~~~~~~~~~ \ell \in f^{-1}(l), \\
     ~~~~~~~~~~~~ l \in internal(G^A.V), ~rc =  \\
     ~~~~~~~~~~~~~~~ [~ pfx \rightarrow [~ ma ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A, \\
     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A,M), \\
     ~~~~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ BS=\{B ~\vert~ (B,q_N) \in pin \}, BS \neq \emptyset \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A,M) \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ ma = \Pref^A(M) : (in,q_N) \rightarrow (out,q_M) ~] ~] ~] \\
  \end{array} \]%

  We now apply the definition of $\Con$ to push it further inside:

      \[ \begin{array}{l}
     ~~~~~ [~ \ell \rightarrow rc ~\vert~ \\
     ~~~~~~~~~~~~ \ell \in f^{-1}(l), \\
     ~~~~~~~~~~~~ l \in internal(G^A.V), ~rc =  \\
     ~~~~~~~~~~~~~~~ \Con([~ pfx \rightarrow [~ ma ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A, \\
     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A,M), \\
     ~~~~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ BS=\{B ~\vert~ (B,q_N) \in pin \}, BS \neq \emptyset \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A,M) \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ ma = \Pref^A(M) : (in,q_N) \rightarrow (out,q_M) ~] ~], \Gamma, f, G) ~] \\
  \end{array} \]%

  Once again, we apply the definition of $\Con$

      \[ \begin{array}{l}
     ~~~~~ [~ \ell \rightarrow rc ~\vert~ \\
     ~~~~~~~~~~~~ \ell \in f^{-1}(l), \\
     ~~~~~~~~~~~~ l \in internal(G^A.V), ~rc =  \\
     ~~~~~~~~~~~~~~~ [~ pfx \rightarrow [~ ma ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A, \\
     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A,M), \\
     ~~~~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ BS=\{B ~\vert~ (B,q_N) \in pin \}, BS \neq \emptyset \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A,M) \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ ma = \Con(\Pref^A(M) : (in,q_N) \rightarrow (out,q_M), true, \ell, \Gamma, f, G) ~] ~] ~] \\
    \end{array} \]%

    Next, we rewrite the sets $in$ and $out$ according to $\Con$:

      \[ \begin{array}{l}
     ~~~~~ [~ \ell \rightarrow rc ~\vert~ \\
     ~~~~~~~~~~~~ \ell \in f^{-1}(l), \\
     ~~~~~~~~~~~~ l \in internal(G^A.V), ~rc =  \\
     ~~~~~~~~~~~~~~~ [~ pfx \rightarrow [~ ma ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A, \\
     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A,M), \\
     ~~~~~~~~~~~~~~~~~~~~~ (\Con(in,\ell,\Gamma,f,G),q_N) \leftarrow \{ (BS,q_N) ~\vert~ BS=\{B ~\vert~ (B,q_N) \in pin \}, BS \neq \emptyset \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \Con(\{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A,M) \}, \ell,\Gamma,f,G), \\
     ~~~~~~~~~~~~~~~~~~~~~ ma = \Con(\Pref^A(M) : (in,q_N) \rightarrow (out,q_M), true, \ell, \Gamma, f, G) ~] ~] ~] \\
  \end{array} \]%

  Rewrite $\Con$ in the set $in$:

    \[ \begin{array}{l}
     ~~~~~ [~ \ell \rightarrow rc ~\vert~ \\
     ~~~~~~~~~~~~ \ell \in f^{-1}(l), \\
     ~~~~~~~~~~~~ l \in internal(G^A.V), ~rc =  \\
     ~~~~~~~~~~~~~~~ [~ pfx \rightarrow [~ ma ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A, \\
     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A,M), \\
     ~~~~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ BS=\Con(\{B ~\vert~ (B,q_N) \in pin \}, \ell, \Gamma, f, G), BS \neq \emptyset \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \Con(\{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A,M) \}, \ell,\Gamma,f,G), \\
     ~~~~~~~~~~~~~~~~~~~~~ ma = \Con(\Pref^A(M) : (in,q_N) \rightarrow (out,q_M), true, \ell, \Gamma, f, G) ~] ~] ~] \\
  \end{array} \]%

  Apply the definition of $\Con$ on the inner set of $in$ and $out$:

    \[ \begin{array}{l}
     ~~~~~ [~ \ell \rightarrow rc ~\vert~ \\
     ~~~~~~~~~~~~ \ell \in f^{-1}(l), \\
     ~~~~~~~~~~~~ l \in internal(G^A.V), ~rc =  \\
     ~~~~~~~~~~~~~~~ [~ pfx \rightarrow [~ ma ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A, \\
     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A,M), \\
     ~~~~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ BS=\{b ~\vert~ b \in f^{-1}(B), (b,\ell)\in G.E, (B,q_N) \in pin \}, BS \neq \emptyset \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ c ~\vert~ c \in f^{-1}(C), (c,\ell)\in G.E, (C,\_) \in \text{adjOut}(PG^A,M) \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ ma = \Con(\Pref^A(M) : (in,q_N) \rightarrow (out,q_M), true, \ell, \Gamma, f, G) ~] ~] ~] \\
  \end{array} \]%

  From Lemma 10, this is equivalent to the following:

    \[ \begin{array}{l}
     ~~~~~ [~ l \rightarrow rc ~\vert~ \\
     ~~~~~~~~~~~~ l \in internal(G.V), ~rc =  \\
     ~~~~~~~~~~~~~~~ [~ pfx \rightarrow [~ ma ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~~~~ m \leftarrow (l,q_m) \in PG, \\
     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG,m), \\
     ~~~~~~~~~~~~~~~~~~~~~ (in,q_n) \leftarrow \{ (bs,q_n) ~\vert~ bs=\{b ~\vert~ (b,q_n) \in pin \}, bs \neq \emptyset \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG,m) \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ ma = \Pref^A(f_{pg}(m)) : (in,q_) \rightarrow (out,q_m) ~] ~] ~]\\
  \end{array} \]%

  From Definition 2, we know that the $\Pref(m) = \Pref(f_{pg}(m))$:

    \[ \begin{array}{l}
     ~~~~~ [~ l \rightarrow rc ~\vert~ \\
     ~~~~~~~~~~~~ l \in internal(G.V), ~rc =  \\
     ~~~~~~~~~~~~~~~ [~ pfx \rightarrow [~ ma ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~~~~ m \leftarrow (l,q_m) \in PG, \\
     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG,m), \\
     ~~~~~~~~~~~~~~~~~~~~~ (in,q_n) \leftarrow \{ (bs,q_n) ~\vert~ bs=\{b ~\vert~ (b,q_n) \in pin \}, bs \neq \emptyset \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG,m) \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ ma = \Pref(m) : (in,q_n) \rightarrow (out,q_m) ~] ~] ~]\\
  \end{array} \]%

  This is exactly the result we obtained from expanding the right hand side of the equality.

  \vspace{.4em}
  \textbf{Case} ($t = \$x$)
  \vspace{.4em}

    The case for $t = \$x$ follows a similar line of reasoning. We start by evaluating the right-hand side:

    \[
    \begin{array}{llll}
      & & \Compile(\Con(p,\Gamma,f),G) \\
      &=& \Compile(\Con(\$x \Path~ r_1 ~\Prefer~ \ldots ~\Prefer~ r_n, \Gamma,f), G) 
            & \text{Substitution} \\
      &=& \Compile([pfx \Path~ \Con(r_1,\Gamma,f) \cap \EndR(l) ~\Prefer~ \ldots ~\Prefer~ \Con(r_n, \Gamma,f) \cap \EndR(l) ~\vert~ (pfx,l) \in \Gamma(x)], G) 
            & \text{Definition of con} \\
      &=& \CompileMbgp([\CompilePg(pfx \Path~ \Con(r_1,\Gamma,f) \cap \EndR(l) ~\Prefer~ \\
      & & ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ \ldots ~\Prefer~ \\ 
      & & ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ \Con(r_n, \Gamma,f) \cap \EndR(l),G) ~\vert~ (pfx,l) \in \Gamma(x)]) 
            & \text{Definition of compile} \\

      &=& \CompileMbgp([(pfx_1, PG_1, \Pref_1), \ldots, (pfx_k, PG_k, \Pref_k)]) 
            & \text{Assumption} \\

    \end{array}
    \]

    Expanding further, this becomes:

      \[ \begin{array}{l}
     ~~~~~ [~ l \rightarrow rc ~\vert~ \\
     ~~~~~~~~~~~~ l \in internal(G.V), ~rc = append_i \\
     ~~~~~~~~~~~~~~~ [~ pfx_i \rightarrow [~ ma ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~~~~ m \leftarrow (l,q_m) \in PG_i, \\
     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG_i,m), \\
     ~~~~~~~~~~~~~~~~~~~~~ (in,q_n) \leftarrow \{ (bs,q_n) ~\vert~ bs=\{b ~\vert~ (b,q_n) \in pin \}, bs \neq \emptyset \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_i,m) \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ ma = \Pref(m) : (in,q_n) \rightarrow (out,q_m) ~] ~] ~]\\
  \end{array} \]%

    As before, we now show that the right hand side is equivalent by applying the definitions of $\Con$ and $\Compile$:

        \[
    \begin{array}{llll}
      & & \Con(\Compile(p,G^A),\Gamma,f,G) \\
      &=& \Con(\Compile(\$x \Path~ r_1 ~\Prefer~ \ldots ~\Prefer~ r_n,G^A),\Gamma,f,G)
            & \text{Substitution} \\
      &=& \Con(\CompileMbgp([\CompilePg(\$x \Path~ r_1 ~\Prefer~ \ldots ~\Prefer~ r_n,G^A)]),\Gamma,f,G)
            & \text{Definition of Compile} \\
      &=& \Con(\CompileMbgp([(pfx,PG^A,\Pref^A)]),\Gamma,f,G)
            & \text{Assumption}\\
    \end{array}
    \]

  Next we further expand on the left side for the abstract topology to show it is equivalent:

  \[ \begin{array}{l}
     ~~~~~ \Con([~ l \rightarrow rc ~\vert~ \\
     ~~~~~~~~~~~~ l \in internal(G^A.V), ~rc =  \\
     ~~~~~~~~~~~~~~~ [~ pfx \rightarrow [~ ma ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A, \\
     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A,M), \\
     ~~~~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ BS=\{B ~\vert~ (B,q_N) \in pin \}, BS \neq \emptyset \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A,M) \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ ma = \Pref^A(M) : (in,q_N) \rightarrow (out,q_M) ~] ~] ~], \Gamma, f, G) \\
  \end{array} \]%

\vspace{5em}
\todo{---------------- OLD STUFF -------------------}
\begin{thm}
  For any context $\Gamma$, concrete topology $G$, abstract topology $G^A$, homomorphism $f : G \rightarrow G^A$:
